### 2017-04-16 paper/oopsla17-submission/evaluation.tex
tweak

\mysection{Quantitative Evaluation}
\label{sec:evaluation}
\input{data}

@@

\mypara{1. Data beats Algorithms}
Our main result is that for type error
localization, data is indeed unreasonably
effective~\citep{halevy09}.
%
\toolname's most sophisticated
\emph{neural network}
based classifier's top-1 error
location blames the correct
sub-term 74\% of the time
which, a good 18 points
higher than the state of
the art \sherrloc's 56\%.
%
However, even \toolname's simple
\emph{logistic regression} based
classifier is correct 60\%,
\ie 4 points better than \sherrloc.
%
When the top-3 locations are considered,
\toolname is correct 91\% of the time.

% \item \textbf
\mypara{2. Slicing is Critical}
%
However, data is effective \emph{only}
when irrelevant sub-terms have been
sliced out of consideration.
%
In fact, perhaps our most surprising
result is that type-error-slicing and
local syntax alone yields
a neural classifier that is 10 points
better than \ocaml and on par with
\sherrloc.
%
That is once we focus classifiers on
slices, purely syntactic features
alone perform as well as the
state-of-the-art.

%\item \textbf
\mypara{3. Size doesn't matter, types do}
%
We find that (after slices)
contextual typing features
provide the biggest
improvement in accuracy.
%
Furthermore we find contextual syntax
features to be relatively unimportant,
which would support the hypothesis that
the context's \emph{type} nicely
summarizes the properties of the
surrounding expressions.
%
Finally, we found that the \emph{size}
of the sub-expression was not a useful
feature. This was unexpected as we thought
smaller expressions would be simpler and
hence, more likely causes.

% \item \textbf
\mypara{4. Models Learn Typing Rules}
%
Finally, by investigating a few of the
predictions made by the \emph{decision tree}
based models, we found that the models
do indeed capture some simple and intuitive
rules for predicting well-typededness.
%
For example, in an application, if the
left argument is a function then the
error is likely on the right sub-term;
in a function definition \RJ{fixme: orig
defining a function is a fine thing
to do?}
%
%\end{itemize}

\RJ{eric please check the numbers -- we say 71, 72, 74, 91, 92, 94?}

>>>>

\mysection{Evaluation}
\label{sec:evaluation}
\input{data}

@@

\mypara{1. Data beats Algorithms}
Our main result is that for type error
localization, data is indeed unreasonably
effective \citep{halevy09}.
%
\toolname's most sophisticated
\emph{neural network}
based classifier's top-1 error
location blames the correct
sub-term 74\% of the time
which, a good 18 points
higher than the state of
the art \sherrloc's 56\%.
%
However, even \toolname's simple
\emph{logistic regression} based
classifier is correct 60\% of the time,
\ie 4 points better than \sherrloc.
%
When the top-3 locations are considered,
\toolname is correct 91\% of the time.

% \item \textbf
\mypara{2. Slicing is Critical}
%
However, data is effective \emph{only}
when irrelevant sub-terms have been
sliced out of consideration.
%
In fact, perhaps our most surprising
result is that type-error-slicing and
local syntax alone yields
a neural classifier that is 10 points
better than \ocaml and on par with
\sherrloc.
%
That is once we focus classifiers on
slices, local syntactic features
alone perform as well as the
state-of-the-art.

%\item \textbf
\mypara{3. Size doesn't matter, types do}
%
We find that (after slices)
contextual typing features
provide the biggest
improvement in accuracy.
%
Furthermore we find contextual syntax
features to be mostly (but not entirely)
redundant with typing features,
which supports the hypothesis that
the context's \emph{type} nicely
summarizes the properties of the
surrounding expressions.
%
Finally, we found that the \emph{size}
of the sub-expression was not very useful.
This was unexpected, as we thought
smaller expressions would be simpler, and
hence, more likely causes.

% \item \textbf
\mypara{4. Models Learn Typing Rules}
%
Finally, by investigating a few of the
predictions made by the \emph{decision tree}-based
models, we found that the models
do indeed capture some simple and intuitive
rules for predicting well-typedness.
%
For example, if the left child of an application
is a function, then the application is likely
correct.

% in an application, if the
% left argument is a function then the
% error is likely on the right sub-term;
% in a function definition
% \RJ{fixme: orig
% defining a function is a fine thing
% to do?}
%
%\end{itemize}
% \RJ{eric please check the numbers -- we say 71, 72, 74, 91, 92, 94?}
